---
title: "Assignment 1"
autor: "Rajesh Chinni"
output: html_document
---

## Answers


**1.** 


**a.** 
```{r}
x <- c(65311 , 65624 , 65908 , 66219 , 66499 , 66821 , 67145 , 67447)
diff(x)
```
Based on the result above, I think the diff(x) function is 313, 284, 311, 280, 322, 324 and 302.


**b.** 
```{r}
length(x)
```

The results suggests that there are 8 values in the vector


**c.** 
```{r}
y <- diff(x)
max(y)
min(y)
mean(y)
sd(y)
```


**2.** 
    
**a.**  
```{r}
Commute <- c(17, 16, 20, 24, 22, 15, 21, 15, 17, 22)
min(Commute)
max(Commute)
mean(Commute)
summary(Commute)
```

**b.** 
```{r}
Commute[4] = 18
mean(Commute)
```

**c.**
```{r}
length(Commute[Commute>= 20])

```

**d.**  
```{r}
length(Commute[Commute < 17])/length(Commute)
```

**e.**

```{r}
Commute + 1
```
The function above adds one to every value in the vector.

```{r}
Commute[-6]
```
The function above shows every value except 6th item in the vector.

```{r}
sum(Commute>21 | Commute<16)
```
The function above shows all values which are either greater than 21 or less than 16 in the vector.

```{r}
Commute[Commute>=17]
```
The function above shows all values which are greater than or equal to 17 in the vector.

```{r}
sum(Commute[Commute>20])
```
The function above shows the total cumulative time of commute of 20 minutes or more.
```{r}
Commute[4:6] 
```
The function above shows 4th, 5th and 6th items of the vector.


```{r}

```


**3.**
```{r}
x <- c(1, 8, 2, 6, 3, 8, 5, 5, 5, 5) 
y = sum(x) /10
print(y)
log10(x)
(x^4.4) / 2.875
max(x)
min(x)
difference <- (max(x) - min(x))
print(difference)

```

**4.** 
  **a.** 
  
```{r}
bill = c(46, 33, 39, 37, 46, 30, 48, 32, 49, 35, 30, 48)
range(bill)
range(bill)[2] - range(bill)[1]
```
The functions above shows highest and smallest value in the vector. Also, the difference of those 2 values.

  **b.** 
  
```{r}
length(bill[bill>40])
length(bill[bill>40])/length(bill)

```

